LaTeX style file for ESANN manuscripts

### 2017-11-25 ESSAN/article.tex
new working example and dynamical range plots

\subsection{Neural Network}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=2.0]{diagram.eps}
\caption{ESANN 2005: Announcement and call for
papers.}\label{Fig:MV}
\end{figure}

Please avoid using DVI2PDF or PS2PDF converters: some undesired
shifting/scaling may occur when using these programs
It is strongly recommended to use the DVIPS converters, and to submit
PS file. You may submit a PDF file if and only if you use ADOBE ACROBAT
to convert your PS file to PDF.
%
Check that you have set the paper size to A4 (and NOT to letter) in your
dvi2ps converter, in Adobe Acrobat if you use it, and in any printer driver
that you could use.  You also have to disable the 'scale to fit paper' option
of your printer driver.
%
In any case, please check carefully that the final size of the top and
bottom margins is 5.2 cm and of the left and right margins is 4.4 cm.
%t is your responsibility to verify this important requirement.  If these margin requirements and not fulfilled at the end of your file generation process, please use the commands at the beginning of the ESANNV2.tex file to correct them.  Otherwise, please do not modify these commands.

\subsection{Additional packages and functions}

Update the sample file according to your text. You can add
packages or declare new \LaTeX\ functions if and only if there is no conflict between your packages and the esannV2.cls style file.

\subsection{Style information}

\subsubsection{Page numbers}
Please do not add page numbers to this style; page numbers will be added by the publisher.
\subsubsection{Page headings}
Do not add headings to your document.
\subsection{Mathematics}
You may include additional packages for typesetting
algorithms, mathematical formula or to define new operators and environments
if and only if there is no conflict with the esannV2.cls
file.

It is recommended to avoid the numbering of equations when not
necessary. When dealing with equation arrays, it could be
necessary to label several (in)equalities. You can do it using the
`$\backslash$stackrel' operator (see the ESANNV2.tex source file);
example:

\begin{eqnarray}
c&=&|d|+|e|\nonumber\\
&\stackrel{\text{(a)}}{=}&d+e\nonumber\\
&\stackrel{\text{(b)}}{\geq}&\sqrt{f}\enspace,
\end{eqnarray}
\noindent where the equality (a) results from the fact that both
$d$ and $e$ are positive while (b) comes from the definition of
$f$.

\subsection{Tables and figures}

Figure \ref{Fig:MV} shows an example of figure and related
caption.  Do not use too small symbols and lettering in your
figures.  Warning: your paper will be printed in black and white
in the proceedings.  You may insert color figures, but it is your
responsibility to check that they print correctly in black and
white.  The color version will be kept in the ESANN electronic
proceedings available on the web.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.6]{ESANN2005BW.eps}
\caption{ESANN 2005: Announcement and call for
papers.}\label{Fig:MV}
\end{figure}

Table \ref{Tab:AgeWeight} shows an example of table.

\begin{table}[h!]
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    ID & age & weight \\
    \hline
    1& 15 & 65 \\
    2& 24 & 74\\
    3& 18 & 69 \\
    4& 32 & 78 \\
    \hline
  \end{tabular}
  \caption{Age and weight of people.}\label{Tab:AgeWeight}
\end{table}

>>>>

\section{The neural network}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=2.0]{diagram.eps}
\caption{The connectivity}\label{Fig:diagram}
\end{figure}

\subsection{A recall example}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{recall.eps}
\caption{A recall example}\label{Fig:recall}
\end{figure}

\section{Dynamic Range}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.25]{dynamical_range.eps}
\caption{The dynamica range}\label{Fig:dynamical_range}
\end{figure}

\section{Learning Rule}

\begin{align}
\tau_w \dfrac{dw}{dt} &= (w_{max} - w) z_{pre}z_{post} + (w_{min} - w) (z_{post} - 1)z_{pre} 
\end{align}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.3]{plasticity_diagram.eps}
\caption{This is how plasticity works}\label{Fig:plasticity diagram}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{training_rule1.eps}
\caption{The training in action}\label{Fig:epochs}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.3]{training_rule_quantities.eps}
\caption{The dynamics of the learning rule}\label{Fig:learning_quantities}
\end{figure}

\section{Disambiguation}

\section{Discussion}
